Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
done editing Sec. V-A

    \subsubsection{Runtime system}

    To simulate the execution of a workflow, we implemented a runtime system.
    It reads the historical data and builds weights for tasks, as explained above.
%    These weights are then treated as the ``truth'' about the execution during the simulation.
    In the static case, these values are being sent to the scheduler, which builds a schedule
    according to these weights.
    However, in the dynamic setting, the runtime system applies a deviation function to the values.
    The deviation function computes a normally distributed deviated value, where the initial value
    is the mean and the deviation is~$10\%$.
    This scenario corresponds to the real-life scenarios identified in~\cite{lotaru} and
    other works dedicated to predicting runtimes of tasks~\cite{da2015online,da2013toward}.

    Hence, the scheduler receives deviated values and makes decision based on them.
    This leads to several types of possible issues:
    \begin{itemize}
        \item A processor is blocked by another task. If the scheduler underestimated the execution time of a task,
        it will block another one from starting.
        \item A predecessor has not yet finished.
        The scheduler may request a task to start on its processor, while
        some of the predecessors of the tasks have in fact not yet completed their execution, and the
        task is therefore not yet ready.
%        A similar situation, but a task could start on its processor, but one or more of its parents a
%        are not ready yet.
        \item Not enough memory. If the scheduler underestimated the amount of memory a task requires, this task might not be able to execute on a chosen processor.
        \item A task took less time than expected. We only consider this case if a task took more than 10\% less
        time than expected. In this
        case, we want to exploit the newly acquired free time by possibly starting other tasks earlier.
    \end{itemize}

>>>>

\subsubsection{Runtime system}
\label{ss:runtime-sys}
%
To simulate the execution of a workflow, we implemented a runtime system.
It reads the historical data and builds weights for tasks as explained above.
%    These weights are then treated as the ``truth'' about the execution during the simulation.
In the static case, these values are being sent to the scheduler, which builds a schedule
according to these weights.
In the dynamic setting, in turn, the runtime system applies a deviation function to the values.
This function computes a normally distributed random deviation value, where the initial value
is the mean and the deviation is~$10\%$.
This scenario corresponds to the real-life scenarios identified in Ref.~\cite{lotaru} and
other works dedicated to predicting task running times~\cite{da2015online,da2013toward}.

Thus, the scheduler receives deviation values and makes decision based on them.
This leads to several types of possible issues:
%
\begin{itemize}
\item 
  A processor is blocked by another task. If the scheduler underestimated the execution time of a task,
  it will block another one from starting.
\item 
  A predecessor has not finished yet.
  The scheduler may request a task to start on its processor, while
  some of the predecessors of the task have in fact not yet completed their execution -- 
  the task is therefore not yet ready.
%        A similar situation, but a task could start on its processor, but one or more of its parents a
%        are not ready yet.
\item 
  Not enough memory. If the scheduler underestimated the amount of memory a task requires, this task might not be able to execute on a chosen processor.
\item 
  A task took less time than expected. We only consider this case if a task took more than 10\% less
  time than expected. In this case, we want to exploit the newly acquired free time by possibly starting other tasks earlier.
\end{itemize}
